Supporting Information

### 2018-04-01 SupportingInformation.Rmd
typo fixed and commented out checkpoint chunk

<!--checkpoint package-->
```{r checkpoint_chunk, echo=F, warning=F, message=F, results="hide"}
library(checkpoint)
#checkloc<-tempdir()
#if (!dir.exists(paste0(checkloc,"/.checkpoint/")))
#{
#  dir.create(paste0(checkloc,"/.checkpoint/"))
#  checkpoint("2018-03-29",checkpointLocation = checkloc)
#}
if (!dir.exists("./.checkpoint/"))
{
  dir.create("./.checkpoint/")
}
checkpoint("2018-03-29",checkpointLocation = "./")
```

@@

### Non-paramtric analysis of tail dependence  \label{Ex_pns_NPA}
```{r stat_plankton_north_sea, echo=F, cache=T, cache.extra=list(seed,data_plankton_north_sea,mtime("NonParamStat.R"))}
set.seed(seed)
resloc<-"./Results/stat_results/stat_plankton_north_sea/"

>>>>

<!--checkpoint package-->
```{r checkpoint_chunk, echo=F, warning=F, message=F, results="hide"}
#library(checkpoint)
#---------------------------------------------------------------
#checkloc<-tempdir()
#if (!dir.exists(paste0(checkloc,"/.checkpoint/")))
#{
#  dir.create(paste0(checkloc,"/.checkpoint/"))
#  checkpoint("2018-03-29",checkpointLocation = checkloc)
#}
#---------------------------------------------------------------
#if (!dir.exists("./.checkpoint/")){
#  dir.create("./.checkpoint/")
#}
#checkpoint("2018-03-29",checkpointLocation = "./")
```

@@

### Non-parametric analysis of tail dependence  \label{Ex_pns_NPA}
```{r stat_plankton_north_sea, echo=F, cache=T, cache.extra=list(seed,data_plankton_north_sea,mtime("NonParamStat.R"))}
set.seed(seed)
resloc<-"./Results/stat_results/stat_plankton_north_sea/"
